A spatio-temporal analysis of the environmental correlates of COVID-19 incidence in Spain

### 2020-04-20 Environmental-Correlates-of-COVID19-Spain/Environmental-Correlates-of-COVID19-Spain.Rmd
Made some revisions based on Fernando's comments about the lag between the lockdown and its effect.

We begin our discussion with the evolution of the spatial autocorrelation coefficient ($\rho$) in Figure \ref{fig:results-time-1} (left panel). It is interesting to note that the magnitude of the spatial autocorrelation coefficient $\rho$ declines over the period under analysis, and is not significant for some days. This is an interesting result: immediately prior to the declaration of the state of emergency, there appears to have been a strong inter-provincial contagion effect. This situation persisted for a few days after the lockdown, and became less strong over time. At the end of the period under examination, the strength of this effect was much diminished. We would expect that under full compliance with strict lockdown conditions (meaning no inter-provincial mobility) the spatial contagion effect would be zero. The fact that it is not is evidence of some weak contagion effect due to restrictions to the movement between provinces.

>>>>

We begin our discussion with the evolution of the spatial autocorrelation coefficient ($\rho$) in Figure \ref{fig:results-time-1} (left panel). It is interesting to note that the magnitude of the spatial autocorrelation coefficient $\rho$ declines over the period under analysis, and is not significant for some days. This is an interesting result: immediately prior to the declaration of the state of emergency, there appears to have been a strong inter-provincial contagion effect. Keeping in mind that the incubation period ranges between 2 and 11 days with a median of 5, it is reasonable to expect that the effect of the lockdown will be observed with some delay. Indeed, as seen in the figure, the autocorrelation coefficient remains high for three days, then declines on March 16, and continues to weaken over time. At the end of the period under examination, the strength of this effect is much diminished. We would expect that under full compliance with strict lockdown conditions (meaning no inter-provincial mobility) the spatial contagion effect would be zero. The fact that it is not is evidence of some weak contagion effect due to restrictions to the movement between provinces.
